Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013},
PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific
Python stack for providing data preparation, manipulation, analysis
and display packages.  This work was supported by NASA award
NNX13AE03G S01 funded through NASA ROSES NNH12ZDA001N-SHP.

@@

Hence, the number of effectively independent pixels time-series must
be calculated.  First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lags $\tau$.  This is used to define a coefficient of independence
between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 times and the mean value $\hat{\rho}$ is
calculated. The effective number of independent pixels in region is
given by
\begin{equation}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{eff}$ in
Equation \ref{eqn:sigmamean}.  The value $\sigma_{mean}$ is used as
the estimate of the error in the \Fps.  Table \ref{tab:neff} shows the
number of pixels in the region and the estimated number of effective
pixels.

\begin{deluxetable}{cc}
\tabletypesize{\scriptsize}
\tablecaption{Number of pixels and effectively independent pixels as a function of region and waveband, as calculated following the procedure of Section \ref{sec:app:ind}. \label{tab:neff}}
\tablewidth{0pt}
\tablehead{
\colhead{Region} &
\colhead{$N_{pixel}$} &
\colhead{Waveband} &
\colhead{$N_{eff}$} &
}
\startdata
loop footpoints & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
moss            & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
quiet Sun       & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
sunspot         & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
\enddata
\end{deluxetable}

\subsection{Model fitting and selection}
The \mFpa\ are assumed to be normally distributed with a width given by
$\sigma_{mean}$ as calculated above.
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).  A five step fitting
process is used to fit Models 1 and 2 to the data.  Maximum likelihood
estimates are found using scipy's maximum likelihood estimators

>>>>

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013},
PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
\citep{Hunter:2007} and Scientific Python stack for providing data
preparation, manipulation, analysis and display packages.  This work
was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
NNH12ZDA001N-SHP.

@@

Hence, the number of effectively independent pixels time-series must
be calculated.  First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lags $\tau$.  This is used to define a coefficient of independence
between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 times and the mean value $\hat{\rho}$ is
calculated. The effective number of independent pixels in region is
given by
\begin{equation}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{eff}$ in
Equation \ref{eqn:sigmamean}, and that value of $\sigma_{mean}$ is
used as the estimate of the error in the \Fps.  Table \ref{tab:neff}
shows the number of pixels in the region and the estimated number of
effective pixels.
\begin{deluxetable}{cccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Number of pixels and
  effectively independent pixels as a function of region and waveband,
  as calculated following the procedure of Section
  \protect\ref{sec:app:ind}. \label{tab:neff}}
\tablehead{
\colhead{Region} &
\colhead{$N_{pixel}$} &
\colhead{Waveband} &
\colhead{$N_{eff}$} \\
}
\startdata
loop footpoints & 2000 & 171\AA & 183 \\
                &     & 193\AA & 185 \\
moss            & 2100 & 171\AA & 629 \\
                &     & 193\AA & 521 \\
quiet Sun       & 2500 & 171\AA & 598 \\
                &     & 193\AA & 639 \\
sunspot         & 7500 & 171\AA & 1505 \\
                &     & 193\AA & 1531 \\
\enddata
\end{deluxetable}

\subsection{Model fitting and selection}
The \mFpa\ are assumed to be normally distributed with a width given
by $\sigma_{mean}$ as calculated above.  Equations \ref{eqn:pwrlaw}
and \ref{eqn:pwrlawbump} are fit to the geometric mean power spectra
shown in Figures \ref{fig:fit171193}.  A five step fitting process is
used to fit Models 1 and 2 to the data. The maximum likelihood
function is constructed using PyMC version 2.3
\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}. Maximum likelihood
estimates are found using SciPy version 0.13.2 \citep{scipy,
  scientificpython} via Powell's minimization method
\citep{Powell01011964, wpress86:numerical}.
